Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-07 thesis/paper.tex
Updated comments for validity threats

\smallskip \noindent
\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types} \cite{lehman1980programs}. Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis. This means that the evolution of the API was studied during a rather short part of its lifetime ( "rephrase"). It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes. We consider this to be remaining threats to construct validity.

@@

\smallskip \noindent
\textbf{Reliability  } Potential threats to the reliability of our study have to a great extent been reduced by conducting the study according to a well-reputed guide to case studies \cite{runeson2009guidelines}. In addition to that, fragments ( "werd") from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} have been used to increase the trustworthiness of the data gathering and data analysis. The analysis was based around well-defined theories that are cemented in academia, to further increase the reproducibility of the study. The semi-structured nature of the interiew, might threaten the reproducibility; but large parts of it were also structured around existing theories.

>>>>

\smallskip \noindent
\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types} \cite{lehman1980programs}. Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis. This means that the evolution of the API was studied during a rather short period of its lifetime ( "Is that better?"). It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes. We consider this to be remaining threats to construct validity. (``not sure about that last sentence'')

@@

\smallskip \noindent
\textbf{Reliability  } Potential threats to the reliability of our study have, to a great extent, been reduced by conducting the study according to a well-reputed guide to case studies \cite{runeson2009guidelines}. In addition to that, (``Concepts, strategies, ideas, techniques'') from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} have been used to increase the trustworthiness of the data gathering and data analysis. The analysis was based around well-defined theories that are cemented in academia, to further increase the reproducibility of the study. The semi-structured nature of the interview, might threaten the reproducibility; however, large parts of it were structured around existing theories.
